---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

## 两个表合并
```{r}
library(tidyverse)
library(nycflights13)

x <- tribble(
  ~key, ~val_x,
     1, "x1",
     2, "x2",
     3, "x3"
)
y <- tribble(
  ~key, ~val_y,
     1, "y1",
     2, "y2",
     4, "y3"
)

x %>% 
  inner_join(y, by = "key")

x %>%
  left_join(y, by = "key")

x %>%
  right_join(y, by = "key")

x %>%
  full_join(y, by = "key")

```

|dplyr|merge|
| ------ | ------ |
|inner_join(x, y)|merge(x, y)|
|left_join(x, y)|merge(x, y, all.x = TRUE)|
|right_join(x, y)|merge(x, y, all.y = TRUE)|
|full_join(x, y)|merge(x, y, all.x = TRUE, all.y = TRUE)|

|dplyr|SQL|
| ------ | ------ |
|inner_join(x, y, by = "z")|SELECT * FROM x INNER JOIN y USING (z)|
|left_join(x, y, by = "z")|merge(SELECT * FROM x LEFT OUTER JOIN y USING (z)|
|right_join(x, y, by = "z")|SELECT * FROM x RIGHT OUTER JOIN y USING (z)|
|full_join(x, y, by = "z")|SELECT * FROM x FULL OUTER JOIN y USING (z)|

## %in%使用方法，识别元素是否属于向量
```{r}

top_dest <- flights %>%
  count(dest, sort = TRUE) %>%
  head(10)

flights %>% 
  filter(dest %in% top_dest$dest)
```
## 两个表对比
```{r}
df1 <- tribble(
  ~x, ~y,
   1,  1,
   2,  1
)
df2 <- tribble(
  ~x, ~y,
   1,  1,
   1,  2
)

intersect(df1, df2)
union(df1, df2)
setdiff(df1, df2)
setdiff(df2, df1)
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
