---
title: "三门模拟问题"
output: html_document
---

## 三门问题


```{r,echo=FALSE,results='hide'}
x <- sample(c(1,2,3), size = 50, replace = T)


## 不换门的概率
mean(x==1)


## 换门的概率模拟计算
Set <- c(1,2,3)

x <- sample(Set,1)
Set[Set != 1 & Set != x]
setdiff(Set,c(x,1))
rep(setdiff(Set,c(x,1)),2)
y <- sample(rep(setdiff(Set,c(x,1)),2),1)
z <- setdiff(Set,c(x,y))

#table(.Last.value)
.Last.value

```

```{r message=FALSE, warning=TRUE, paged.print=FALSE}

z_chouyan <- function(x){
  a <- 1:3
  x <- sample(a,1)
  temp <- a[a!=1 & a!=x]
  y <- ifelse(length(temp) == 1, temp, sample(x = temp, size = 1))
  setdiff(a,c(x,y))
}

n <- 1000
mean(sapply(rep(1,n), z_chouyan) ==1)

```

```{r}
#寻找x个人中，出现两个或两个以上同个月份生日的概率
moths=12
brithday <- function(num, times=500){
  x <- replicate(times,{
    temp <- table(sample(1:12,num,replace = T))
    any(temp >1)
    })
  mean(x)
}
brithday(4)
```






Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
